Late Pleistocene stone artefact technology at Mau A, Yen Bai, Norther Vietnam

### 2022-02-11 analysis/paper/paper.Rmd
add in code block that does the univariate k-means

<!--QH: I have been fiddling about with code and github for awhile. I plan on fixing everything when I wake up, and, failing that, Friday afternoon.-->
```{r}
ma_flakes_tr_with_groups <-
  ma_flakes_tr %>%
  mutate(dorsal_cortext_group = as.factor(
           case_when(
             between(dorsal_cortex_perc, 0, 0) ~ "Tertiary",
             between(dorsal_cortex_perc, 1, 50) ~ "Secondary",
             between(dorsal_cortex_perc, 51, 100) ~ "Primary"
           ))) %>% 
 mutate(mass_group = as.factor(test_result_mass$cluster))
# plot mass groups
ggplot(ma_flakes_tr_with_groups)  +
  aes(mass,
      fill = mass_group) +
  geom_histogram() +
  scale_fill_viridis_d(name = "Mass\ncluster") +
  xlab("Mass (g)") +
  theme_minimal(base_size = 14) +
  theme(panel.background = element_rect(fill='white',
                                        colour = "white"),
        plot.background = element_rect(fill='white',
                                       colour = "white"))

>>>>

<!--QH: I have been fiddling about with code and github for awhile. I plan on fixing everything when I wake up, and, failing that, Friday afternoon.-->

```{r}
library(Ckmeans.1d.dp)

test_result_dorsal_cortex <- Ckmeans.1d.dp(ma_flakes_tr$dorsal_cortex_perc)

plot(test_result_dorsal_cortex)

# It seems that there is no clear clustering in the Dorsal Cortex values. I will have to use values from the literature to divide the cortex values

# try mass:
test_result_mass <- Ckmeans.1d.dp(ma_flakes_tr$mass)

# plot(test_result_mass)
# we got six clusters
```

```{r}
ma_flakes_tr_with_groups <-
  ma_flakes_tr %>%
  mutate(dorsal_cortext_group = as.factor(
           case_when(
             between(dorsal_cortex_perc, 0, 0) ~ "Tertiary",
             between(dorsal_cortex_perc, 1, 50) ~ "Secondary",
             between(dorsal_cortex_perc, 51, 100) ~ "Primary"
           ))) %>% 
 mutate(mass_group = as.factor(test_result_mass$cluster))

# plot mass groups
ggplot(ma_flakes_tr_with_groups)  +
  aes(mass,
      fill = mass_group) +
  geom_histogram() +
  scale_fill_viridis_d(name = "Mass\ncluster") +
  xlab("Mass (g)") +
  theme_minimal(base_size = 14) +
  theme(panel.background = element_rect(fill='white',
                                        colour = "white"),
        plot.background = element_rect(fill='white',
                                       colour = "white"))
